Reinforcement Learning in Network Defence/Control (WIP)

### 2018-04-09 interim-talk/interim-talk.tex
Some minor changes.

\begin{frame}{The capabilities of attackers}
	\begin{itemize}
		\item Evasion for \emph{polymorphic blending attacks} (i.e., evasion) on past models are known \NP-Complete\footcite{DBLP:conf/ccs/FoglaL06}.

@@

		\item Careless model exposure $\implies$ black-box model extraction\footcite{DBLP:conf/uss/TramerZJRR16} $\implies$ evasion\footcite{DBLP:conf/sp/Carlini017}.

@@

\begin{frame}{Unknowns}
	\begin{itemize}
		\item We don't have results for poisoning on e.g., Deep RL in the network.

		\item We also lack results on how/if evasion attacks can transfer for learners focused on non-stationarity/constant learning.

>>>>

\begin{frame}{The capabilities of attackers}
	\begin{itemize}
		\item \emph{Polymorphic blending attacks} (i.e., evasion) on past models are known \alert{\NP-Complete} by reduction to (s)FSA\footcite{DBLP:conf/ccs/FoglaL06}.

@@

		\item Careless model exposure $\implies$ \alert{black-box model extraction}\footcite{DBLP:conf/uss/TramerZJRR16} $\implies$ evasion\footcite{DBLP:conf/sp/Carlini017}.

@@

\begin{frame}{Unknowns}
	\begin{itemize}
		\item We don't have results for poisoning on e.g., Deep RL in the network.
		\begin{itemize}
			\item Can an adversary precisely affect state at all measurement points?
			% Networks are unstable ``bursty'', and attacker has limited control over inbound traffic.
		\end{itemize}

		\item We also lack results on whether evasion attacks can transfer between policies which evolve over time.
		\begin{itemize}
			\item E.g., $\pi_t$ to $\pi_{t+\delta}$ for reinforcement learners focused on non-stationarity.
		\end{itemize}
